Hierarchical Dispatching and Overriding

### 2017-09-16 NewVersion/sections/TypeSafety.tex
Fixing proof.

@@

\noindent \textbf{Case Invk.}
$ e = e_0.m(\overline{e}) \quad
  \judgeewf {\Gamma, \overline{x}:\overline{I_x}} {e_0 : I_0} $
$$ mtype(m, I_0) = \overline{I_e} \rightarrow J $$
$$ \judgeewf {\Gamma, \overline{x}:\overline{I_x}} {\overline{e}:\overline{I}} \quad
    \overline{I} \subtype \overline{I_e} $$
By induction hypothesis, there are some $I_0'$ and $\overline{I_e'}$ such that
    $$ \judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0 : I_0'} \quad 
        I_0' \subtype I_0 $$
    $$ \judgeewf {\Gamma} {[\overline{y}/\overline{x}]\overline{e} : \overline{I_e'}} \quad  
        \overline{I_e'} \subtype \overline{I}$$    
By lemma~\ref{lemma2}, 
    $mtype(m, I_0') = \overline{I_e} \rightarrow J$,
then $\overline{I_e'} \subtype \overline{I_e}$ by the transitivity of $\subtype$.
Therefore, by the rule \textsc{(T-Invk)}, 
    $\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0.m([\overline{y}/\overline{x}]\overline{e}) : J}$.

@@

\noindent \textbf{Case SuperInvk.}
$ e = \kwsuper.I::m(\overline{e}) $ \\
Suppose $\judgeewf {\Gamma} {\kwthis : I_0}$, the following proof should be similar as case Var.
\end{proof}

@@

\subsubsection{Proof for Theorem~\ref{theorem_subject}}
\begin{proof} ~\\
\noindent \textbf{Case Invk.} 
let \[ e = \angl{J}\new I.m(\overline{\angl{I_e}}\overline{e}) \] 
Suppose \[ \mbody(m, I, J) = (J', \overline{I_x} \; \overline{x}, I_{e_0} \; e_0) \] 
then \[ e' =  [\overline{\angl{I_x}} \overline{e}/\overline{x}, \; \angl{J}\new I/\kwthis ] e_0 \] 
By rules \textsc{(T-New)} and \textsc{(T-Invk)}, 
  \[ \judgeewf \Gamma {\new I:I} \quad 
     \mtype(m, I, J) = \overline{I_x} \rightarrow I_{e_0} \quad 
     \judgeewf \Gamma {\overline{e} : \overline{I_e'}} \quad
     \overline{I_e'} \subtype \overline{I_x} \quad
     \textit{, for some } \; \overline{I_e'}
  \]
By Lemma~\ref{lemma0},
    \[
    \judgeewf {\Gamma, \overline{x}:\overline{I_x}, \kwthis:J_0} {e_0:I_f} \textit{, for some } J \subtype J_0 \textit{ and } I_f \subtype I_{e_0}
    \]
By Lemma~\ref{lemma1},
    \[
    \judgeewf {\Gamma} {[\overline{\angl{I_x}} \overline{e}/\overline{x}, \; \angl{J}\new I/\kwthis ] e_0  :  I_g} \textit{, for some } I_g \subtype I_f 
    \]
So $I_g <: I_{e_0}$, finally just let $I' = I_g$.

>>>>

\textcolor{red}{
\begin{lemma}[Method Type Preservation]~\label{lemma2_new}
$\textit{If } \mbody(m, I_0, J_0) = (K, \overline{I_x}\ \overline{x}, I_e\ e)$, $\textit{ and }
\mbody(m, I'_0, J_0) = (K', \overline{I'_x}\ \overline{x'}, I'_e\ e') \textit{ for some }I'_0 \subtype I_0, \textit{ then }
\overline{I'_x} = \overline{I_x}$ $\textit{and } I'_e = I_e.$
\end{lemma}}

@@

\noindent \textbf{Case Invk.}
$ e = e_0.m(\overline{e}) \quad
  \judgeewf {\Gamma, \overline{x}:\overline{I_x}} {e_0 : I_0} $
$$ mtype(m, I_0) = \overline{I_e} \rightarrow J $$
$$ \judgeewf {\Gamma, \overline{x}:\overline{I_x}} {\overline{e}:\overline{I}} \quad
    \overline{I} \subtype \overline{I_e} $$
By induction hypothesis, there are some $I_0'$ and $\overline{I_e'}$ such that
    $$ \judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0 : I_0'} \quad 
        I_0' \subtype I_0 $$
    $$ \judgeewf {\Gamma} {[\overline{y}/\overline{x}]\overline{e} : \overline{I_e'}} \quad  
        \overline{I_e'} \subtype \overline{I}$$    
By lemma~\ref{lemma2}, 
    $mtype(m, I_0') = \overline{I_e} \rightarrow J$.

\noindent Then $\overline{I_e'} \subtype \overline{I_e}$ by the transitivity of $\subtype$.
Therefore, by the rule \textsc{(T-Invk)}, 
    $\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0.m([\overline{y}/\overline{x}]\overline{e}) : J}$.

@@

\noindent \textbf{Case SuperInvk.}
$ e = \kwsuper.I::m(\overline{e}) $ \\
Suppose $\judgeewf {\Gamma} {\kwthis : I_0}$, the following proof should be similar as case Var.

\noindent\textcolor{red}{\textbf{Case PathInvk.} $e = e_0.J_0?m(\overline{e})$. By \textsc{(T-PathInvk)}, suppose}
	$$\textcolor{red}{\judgeewf {\Gamma, \overline{x}:\overline{I_x}} {e_0 : I_0} \quad I_0 \subtype J_0}$$
	$$\textcolor{red}{\mbody(m, I_0, J_0) = (\_, \overline{J}\ \_, I\ \_)}$$
	$$\textcolor{red}{\judgeewf {\Gamma, \overline{x}:\overline{I_x}} {\overline{e} : \overline{I_e}} \quad 
	  \overline{I_e} \subtype \overline{J} \quad \judgeewf {\Gamma, \overline{x}:\overline{I_x}} {e : I}}$$
\textcolor{red}{By induction hypothesis, there are some $I'_0$ and some $\overline{I'_e}$ such that}
	$$\textcolor{red}{\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0 : I_0'} \quad I_0' \subtype I_0 \subtype J_0}$$
	$$\textcolor{red}{\judgeewf {\Gamma} {[\overline{y}/\overline{x}]\overline{e} : \overline{I_e'}} \quad 
	  \overline{I_e'} \subtype \overline{I_e} \subtype \overline{J}}$$   
\textcolor{red}{By lemma~\ref{lemma2_new}, if $[\overline{y}/\overline{x}]e$ is well typed,}
	$$\textcolor{red}{\mbody(m, I'_0, J_0) = (\_, \overline{J}\ \_, I\ \_)}$$
\textcolor{red}{Therefore, by the rule \textsc{(T-Invk)}, 
	$\judgeewf {\Gamma} {[\overline{y}/\overline{x}]e_0.m([\overline{y}/\overline{x}]\overline{e}) : I}$.}

@@

\subsubsection{Proof for Theorem~\ref{theorem_subject}}
\begin{proof} ~\\
\noindent\textcolor{red}{\textbf{Case PathInvk.} Let} \haoyuan{where to use lemma 1}
  $$\textcolor{red}{e = (\angl{J}\new{I}).K?m(\overline{v}) \quad \judgeewf {\Gamma} {e : I_e}}$$
  $$\textcolor{red}{e' = \angl{I_e}[\overline{\angl{I_x}} \overline{v}/\overline{x}, \angl{I_0}\new{I}/\kwthis]e_0 \quad \judgeewf {\Gamma} {e' : I'_e}}$$
  $$\textcolor{red}{\mbody(m, I, K) = (I_0, \overline{I_x} \; \overline{x}, I_e \; e_0)}$$
\textcolor{red}{Since $e$ is well typed, $\angl{J}\new{I}$ is well typed, and}
  $$\textcolor{red}{\judgeewf {\Gamma} {\angl{J}\new{I} : I}}$$
\textcolor{red}{By \textsc{(T-Anno)}, we have $I \subtype J$.}

\noindent\textcolor{red}{Suppose that the original form of $(\angl{J}\new{I}).K?m(\overline{v})$ is $e_T.K?m(\overline{e_T})$ by reduction.
	The original expression should be type-checked already by \textsc{(T-PathInvk)}. Suppose that}
  $$\textcolor{red}{\judgeewf {\Gamma} {e_T : I_T} \quad \judgeewf {\Gamma} {\overline{e_T} : \overline{I_T}}}$$
\textcolor{red}{By induction hypothesis, $I \subtype I_T$. By lemma~\ref{lemma2_new},}
  $$\textcolor{red}{\mbody(m, I_T, K) = (\_, \overline{I_x}\ \_, I_e\ \_)}$$
\textcolor{red}{Therefore $\overline{I_T} \subtype \overline{I_x}$. By induction hypothesis,}
  $$\textcolor{red}{\judgeewf {\Gamma} {\overline{v} : \overline{I_v} \subtype \overline{I_T} \subtype \overline{I_x}}}$$
\textcolor{red}{So the first substitution preserves typing, On the other hand, .... the second one also preserves typing. Hence $I'_e \subtype$ type of $e_0 \subtype I_e$.}

\noindent \textbf{Case Invk.} 
let \[ e = \angl{J}\new I.m(\overline{\angl{I_e}}\overline{e}) \] 
Suppose \[ \mbody(m, I, J) = (J', \overline{I_x} \; \overline{x}, I_{e_0} \; e_0) \] 
then \[ e' =  [\overline{\angl{I_x}} \overline{e}/\overline{x}, \; \angl{J}\new I/\kwthis ] e_0 \] 
By rules \textsc{(T-New)} and \textsc{(T-Invk)}, 
  \[ \judgeewf \Gamma {\new I:I} \quad 
     \mtype(m, I, J) = \overline{I_x} \rightarrow I_{e_0} \quad 
     \judgeewf \Gamma {\overline{e} : \overline{I_e'}} \quad
     \overline{I_e'} \subtype \overline{I_x} \quad
     \textit{, for some } \; \overline{I_e'}
  \]
By Lemma~\ref{lemma0},
    \[
    \judgeewf {\Gamma, \overline{x}:\overline{I_x}, \kwthis:J_0} {e_0:I_f} \textit{, for some } J \subtype J_0 \textit{ and } I_f \subtype I_{e_0}
    \]
By Lemma~\ref{lemma1},
    \[
    \judgeewf {\Gamma} {[\overline{\angl{I_x}} \overline{e}/\overline{x}, \; \angl{J}\new I/\kwthis ] e_0  :  I_g} \textit{, for some } I_g \subtype I_f 
    \]
So $I_g <: I_{e_0}$, finally just let $I' = I_g$.
